toyData

### 2017-11-14 latex/dataMaid_toyData.Rmd
Prep for JSS submission

---
dataMaid: yes
title: toyData
subtitle: "Autogenerated data summary from dataMaid"
date: 2017-11-09 15:41:24
output: pdf_document
documentclass: report
header-includes:
  - \renewcommand{\chaptername}{Part}
  - \newcommand{\fullline}{\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}}
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library(ggplot2)
library(pander)
```
# Data report overview
The dataset examined has the following dimensions:

@@

 *  Report creation time: Thu Nov 09 2017 15:41:24

 *  dataMaid v0.9.7.9000 [Pkg: 2017-11-09 from local (ekstroem/dataMaid@NA)]

@@

 *  Platform: x86_64-apple-darwin15.6.0 (64-bit)(macOS Sierra 10.12.6).

>>>>

---
dataMaid: yes
title: toyData
subtitle: "Autogenerated data summary from dataMaid"
date: 2017-11-14 13:41:55
output: pdf_document
documentclass: report
header-includes:
  - \renewcommand{\chaptername}{Part}
  - \newcommand{\fullline}{\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}}
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library(ggplot2)
library(pander)
```
# Data report overview
The dataset examined has the following dimensions:

@@

 *  Report creation time: Tue Nov 14 2017 13:41:55

 *  dataMaid v1.0.1 [Pkg: 2017-11-13 from local (ekstroem/dataMaid@NA)]

@@

 *  Platform: x86_64-apple-darwin15.6.0 (64-bit)(macOS High Sierra 10.13.1).
